### 2014-03-12 src/introduction.Rnw
update
udpate

However, as pointed out by Zhang et al.~\cite{zhang2013ase}, the
field has a serious lacuna in large scale research, both in the
size of the programs studied, and in the number and diversity of
programs, which reduces our confidence in their results. This is
true for selective mutation studies, studies in sampling, and also
for comparatively newer studies that attempt to combine them. This is
particularly worrisome if mutation analysis is to gain wider acceptance
among testing professionals. Further, quite a few of the influential
studies~\cite{offutt1993experimental,offutt1996anexperimental,wong1995reducing}
has been conducted on older programming languages such as Fortran with
operators specific to it, and are not directly applicable to newer languages
such as Java, with significant differences. Finally, with the modern research
into the ``do-smarter'' approach using byte code based mutation -- eliminating
the compilation step -- operators based on source code modification is no
longer be applicable, and their equivalents in the bytecode needs to be
found and compared with other approaches. A detailed discussion of these
issues can be found in Section~\ref{sec:related}.

@@

\begin{itemize}
\item simpler schemes work better. %Don't try sophisticated schemes. against Zhang's impression future work.
\item Sampling at coarsest level (i.e. project level) gives the best result. % against Zhang's findings
\item Single line sampling gives better results than statement deletion. % comparing random selection and operator selection.
 % SDL has been recommended by Offutt.

\end{itemize}
%We make the following contributions:
%\begin{itemize}
%\item We compare a large number of mutation sampling and selection strategies (Section~\ref{sec:analysis}).
%\item It seek sto improve the statistical confidence in our results by utilizing a much larger sample of projects
%      (188 projects) from the open source repository at Github~\cite{github}, using both original and automatically
%      generated test-suites using Randoop~\cite{randoop} (Section~\ref{sec:methodology}). 
%\item It analyses the results and suggest strategies (Section~\ref{sec:results}).
%\end{itemize}

>>>>

However, as pointed out by Zhang et al.~\cite{zhang2013ase}, the
field has a serious lacuna in large scale research, both in the
size of the programs studied, and in the number and diversity of
programs, which reduces our confidence in their results. This is
true for selective mutation studies, studies in sampling, and also
for comparatively newer studies that attempt to combine them. This is
particularly worrisome if mutation analysis is to gain wider acceptance
among testing professionals. Further, quite a few of the influential
studies~\cite{offutt1993experimental,offutt1996anexperimental,wong1995reducing,mresa1999efficiency}
has been conducted on older programming languages such as Fortran with
operators specific to it, and are not directly applicable to newer languages
such as Java, with significant differences. Finally, with the modern research
into the ``do-smarter'' approach using byte code based mutation -- eliminating
the compilation step -- operators based on source code modification is no
longer be applicable, and their equivalents in the bytecode needs to be
found and compared with other approaches. A detailed discussion of these
issues can be found in Section~\ref{sec:related}.

@@

%We make the following contributions:
%\begin{itemize}
%\item We compare a large number of mutation sampling and selection strategies (Section~\ref{sec:analysis}).
%\item It seek sto improve the statistical confidence in our results by utilizing a much larger sample of projects
%      (188 projects) from the open source repository at Github~\cite{github}, using both original and automatically
%      generated test-suites using Randoop~\cite{randoop} (Section~\ref{sec:methodology}). 
%\item It analyses the results and suggest strategies (Section~\ref{sec:results}).
%\end{itemize}
